The Noisy Work of Uncertainty Visualisation Research: A Review

### 2024-08-19 paper.qmd
fixed table issue (it is what it is)

```{r}
#| echo: false
#| message: false
#| warning: false
#| label: fig-data
#| fig-cap: "The"
#| cap-location: "bottom"

@@

# Make nice example table
example_table <- my_map_data |>
  mutate(variance = sqrt(variance)) |>
  select(c(count_id, county_name, temp, variance_class, variance)) |>
  as_tibble()|>
  pivot_wider(id_cols=c(count_id, county_name, temp,), 
              names_from = variance_class, 
              values_from = variance) |>
  head()|>
  flextable() |>
  set_caption(caption = "Average Daily High Temperatures of Iowa Counties") |>
  add_header_row(colwidths = c(3, 2),
                 values = c("", "Standard Error")) |>
  colformat_double(digits = 2) |>
  set_header_labels(count_id = "ID", 
                    county_name  = "County",
                    temp = "Temperature (°C)",
                    highvar = "High",
                    lowvar = "Low") |>
  theme_vanilla() |>
  vline(i=c(1,2), j=3, part="header")|>
  align(align = "left", part = "all") |>
  bg(j = "temp",
    bg = col_numeric(palette = brewer.pal(8, name = "Oranges"),
                     domain = c(21, 30)),
    part = "body"
  ) |>
  bg(j = c("highvar", "lowvar"),
    bg = col_numeric(palette = brewer.pal(8, name = "Greens"),
                     domain = c(0, 3)),
    part = "body"
  )

@@

example_table

>>>>

```{r}
#| echo: false
#| message: false
#| warning: false
#| label: fig-data
#| fig-cap: "The the first 5 observations of the data used for the spatial uncertainty examples along with the boundaries of each county. The map boundaries are the Iowa county boundaries, however the 'temperature' data is not representative of the average temperature in Iowa. The temperature and standard error represent the average of the daily high temperature and the standard error of that average respectively."
#| fig-subcap: 
#|   - "Data Table"
#|   - "Map Boundaries"
#| layout-nrow: 1
#| cap-location: "bottom"

@@

# Make nice example table
example_table <- my_map_data |>
  mutate(variance = sqrt(variance)) |>
  select(c(count_id, county_name, temp, variance_class, variance)) |>
  as_tibble()|>
  pivot_wider(id_cols=c(count_id, county_name, temp,), 
              names_from = variance_class, 
              values_from = variance) |>
  head(5)|>
  flextable() |>
  set_caption(caption = "Average Daily High Temperatures of Iowa Counties") |>
  add_header_row(colwidths = c(3, 2),
                 values = c("", "Standard Error")) |>
  colformat_double(digits = 2) |>
  set_header_labels(count_id = "ID", 
                    county_name  = "County",
                    temp = "Average Temperature (°C)",
                    highvar = "High",
                    lowvar = "Low") |>
  theme_vanilla() |>
  vline(i=c(1,2), j=3, part="header")|>
  align(align = "left", part = "all") |>
  bg(j = "temp",
    bg = col_numeric(palette = brewer.pal(8, name = "Oranges"),
                     domain = c(21, 30)),
    part = "body"
  ) |>
  bg(j = c("highvar", "lowvar"),
    bg = col_numeric(palette = brewer.pal(8, name = "Greens"),
                     domain = c(0, 3)),
    part = "body"
  )

@@

plot(example_table)
